Helmet Foam Case Study Report

### 2024-04-29 CS2 Final Draft.qmd
Update CS2 Final Draft.qmd
Update CS2 Final Draft.qmd
updated #1.2 again

**Explanatory Variables:**

|    Variable Name    |                   Description                                 |
|:--------------------|:---------------------------------------------------------------------------------------------|
|        ID            |  the unique identifier of the different foam pieces|
|     chemIndex        |  the chemical makeup type of the foam. 1 = 79, 2 = 100, 3 = 121|
|      porosity        |  the porosity level of the foam. Low = 71%, high = 81%|
|       freq           |  the number of compressions per second (hz)|
|        amp           |  the amplitude of the compressions|
|    initialStrain     |  the initial measure of the strain of foam. (Originally labeled “strain”)|
|    initialStress     |  the initial measure of the stress of the foam. (Originally labeled “stresskpa”)|
|       cycle          |  the cycle number the measurement was taken at|

*Caption: Table 1. Explanatory Variables*

**Response Variables:**

|    Variable Name    |                   Description                                       |
|:--------------------|:---------------------------------------------------------------------------------------------|
|     stiffness        |  measurement of the foam’s stiffness. (Originally labeled “E1_MPA”)|
|      damping         |  measurement of the foam’s damping. (Originally labeled “delta_rad”)|
|    stiffnessFrac     |  stiffness / first stiffness measurement|
|     dampingFrac      |  tan(damping) / tan(first damping measurement)|

*Caption: Table 2. Response Variables*

@@

$\log(\text{stiffnessFrac}) = \alpha_0 + \alpha_1*I(\text{porosity} = \text{low})) + \alpha_2*I(\text{chemIndex} = 2)$\newline
$+\alpha_3*I(\text{chemIndex} = 3)+\alpha_4*I(\text{chemIndex} = 2)*I(\text{porosity} = low)$\newline
$+\alpha_5*I(\text{chemIndex} = 3)*I(\text{porosity} = low)+\beta_0*\log(\text{cycle}) +  \beta_1*\log(\text{cycle})*I(\text{porosity} = \text{low})$\newline
$+\beta_2*\log(\text{cycle})*I(\text{chemIndex} = 2)+\beta_3*\log(\text{cycle})*I(\text{chemIndex} = 2)*I(\text{porosity} = \text{low})$\newline
$+\beta_4*\log(\text{cycle})*I(\text{chemIndex} = 3)*I(\text{porosity} = \text{low})+ u_i + v_i*\log(\text{cycle}) + \epsilon_{ij}$

@@

$\log(\text{dampingFrac}) = \alpha_0 + \alpha_1*I(\text{porosity} = \text{low}) + \alpha_2*I(\text{chemIndex} = 2) + \alpha_3*I(\text{chemIndex} = 3)$\newline
$+\alpha_4*\text{freq} + \beta_0*\log(\text{cycle}) + \beta_1*(I(\text{porosity} = \text{low})*\log(\text{cycle}))$\newline
$+\beta_3*(I(\text{chemIndex} = 2)*\log(\text{cycle})) + \beta_4*(I(\text{chemIndex} = 3)*\log(\text{cycle}))$\newline
$+\beta_5*(\text{freq}*\log(\text{cycle})) + u_i + v_i*\log(\text{cycle}) + \epsilon_{ij}$.

>>>>

\begin{center}
\textbf{Explanatory Variables:}
\end{center}

\begin{center}
\begin{tabular}{|l|l|}
\hline
\text{Variable Name} & \text{Description} \\
\hline
ID & the unique identifier of the different foam pieces \\
chemIndex & the chemical makeup type of the foam. 1 = 79, 2 = 100, 3 = 121 \\
porosity & the porosity level of the foam. Low = 71\%, high = 81\% \\
freq & the number of compressions per second (hz) \\
amp & the amplitude of the compressions \\
initialStrain & the initial measure of the strain of foam. (Originally labeled ``strain'') \\
initialStress & the initial measure of the stress of the foam. (Originally labeled ``stresskpa'') \\
cycle & the cycle number the measurement was taken at \\
\hline
\end{tabular}
\end{center}

\begin{center}
\text{Table 1: Explanatory Variables}
\end{center}

\begin{center}
\textbf{Response Variables}
\end{center}

\begin{center}
\begin{tabular}{|l|l|}
\hline
\text{Variable Name} & \text{Description} \\
\hline
stiffness & measurement of the foam’s stiffness. (Originally labeled ``E1\_MPA'') \\
damping & measurement of the foam’s damping. (Originally labeled ``delta\_rad'') \\
stiffnessFrac & stiffness / first stiffness measurement \\
dampingFrac & tan(damping) / tan(first damping measurement) \\
\hline
\end{tabular}
\end{center}

\begin{center}
\text{Table 2: Response Variables}
\end{center}

@@

Level 1: $\log(\text{stiffnessFrac}) = \alpha_i + \beta_i*log(cycle)$
Level 2: $\alpha_i = \alpha_0 + \alpha_1*\text{porosity} + \alpha_2*\text{chemIndex} + \alpha_3*\text{freq} + \alpha_4*\text{amp}$
         $\beta_i = \beta_0 + \beta_1*\text{porosity} + \beta_2*\text{chemIndex} +\beta_3*\text{freq} + \beta_4*\text{amp}$

@@

Level 1: $\log(\text{dampingFrac}) = \alpha_i + \beta_i*log(cycle)$
Level 2: $\alpha_i = \alpha_0 + \alpha_1*\text{porosity} + \alpha_2*\text{chemIndex} + \alpha_3*\text{freq}$
         $\beta_i = \beta_0 + \beta_1*\text{porosity} + \beta_2*\text{chemIndex} +\beta_3*\text{freq}$
